---
title: "Project"
author: "Kiyoon Jeong"
date: "December 2, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(stringr)
library(choroplethr)

setwd("C:/Users/Kiyoon Jeong/Desktop/wrangling_project")

url <- "https://en.wikipedia.org/wiki/List_of_countries_by_suicide_rate"

url_table <- url %>% read_html() %>% html_nodes("table") %>% .[[2]] %>% html_table(fill = TRUE)

url_table$Country <-  str_replace(url_table$Country , "\\ \\([ a-z]+\\)" , "")

url_table$Country <-  as.character(str_extract_all(url_table$Country , "([ A-z ]+)"))

url_table$Country[51] <- "united states of america"

url_table$Country <- tolower(url_table$Country)

colnames(url_table)[2] <- "region"

colnames(url_table)[3] <- "Both"

## 1. Both

df_country <- subset(url_table, select = c(region, Both))

colnames(df_country)[2] <- "value"

country_choropleth(df_country)

## 2. Male

df_country <- subset(url_table, select = c(region, Male))

colnames(df_country)[2] <- "value"

country_choropleth(df_country)

## 3. Female

df_country <- subset(url_table, select = c(region, Female))

colnames(df_country)[2] <- "value"

country_choropleth(df_country)

```



```{r}
library(dplyr)
library(ggplot2)
df1 <- read.csv("AV_AN_WAGE_17112016232031509.csv")
df2 <- read.csv("AVE_HRS_17112016230809134.csv")

df <- inner_join(df1, df2, by = c("Country"="Country", "Time" = "Time"))

df_select <- subset(df , select = c(Country, Time, Value.x , Value.y))

colnames(df_select)[3] <- "Income"

colnames(df_select)[4] <- "WorkHour"

## Year vs Working hour

df_select %>% ggplot(aes(x = Time, y = WorkHour , colour = Country)) + xlab("Yeaer") + ylab("Weekly Working Hour") + geom_line()

## Year vs Income

df_select %>% ggplot(aes(x = Time, y = Income , colour = Country)) + xlab("Year") + ylab("Income") + geom_line()

```

## shiny app

```{r}

library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      sliderInput("TimeInput", "Time", min = 2000, max = 2014, value = c(2000, 2014)),
      selectInput("nameInput", "Choose a country:", choices = df_select$Country),
    mainPanel(
      plotOutput("main_plot"),
      tableOutput("results")
    )
  ),
  titlePanel("Working Hour versus Income")
))
server <- function(input, output, session) {
  reduced_df <- reactive({
    filter(
      df_select, 
      Country == input$nameInput, 
      Time >= input$TimeInput[1] & Time <= input$TimeInput[2]
    )
  })
  output$main_plot <- renderPlot({
      ggplot(data = reduced_df(), 
             aes(WorkHour, Income, colour = Country)) + 
        geom_line() + ggtitle(input$nameInput)
    
  })
  output$results <- renderTable({ 
      reduced_df()
  })
}

shinyApp(ui = ui, server = server)

```

library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      sliderInput("TimeInput", "Time", min = 2000, max = 2014, value = c(2000, 2014)),
      selectInput("nameInput", "Choose a country:", choices = df_select$Country),
    mainPanel(
      plotOutput(outputId = "main_plot", width = "500%"),
      tableOutput("results")
    )
  ),
  titlePanel("Working Hour versus Income")
))
server <- function(input, output, session) {
  reduced_df <- reactive({
    filter(
      df_select, 
      Country == input$nameInput, 
      Time >= input$TimeInput[1] & Time <= input$TimeInput[2]
    )
  })
  output$main_plot <- renderPlot({
      ggplot(data = reduced_df(), 
             aes(WorkHour, Income, colour = Country)) + 
        geom_line() + ggtitle(input$nameInput)
    
  })
  output$results <- renderTable({ 
      reduced_df()
  })
}

shinyApp(ui = ui, server = server)


##ggplot

```{r}

df_select %>% ggplot(aes(x = WorkHour, y = Income , colour = Country)) + xlab("Weekly Working Hour") + ylab("Income") + geom_line()

```

##merge data

```{r}

df_select$Country <- tolower(df_select$Country)

df_select$Country <- str_replace_all(df_select$Country , "korea" , "south korea")

df_select1 <- df_select %>% group_by(Country) %>% summarise(avgIncome = mean(Income))

df_select2 <- df_select %>% group_by(Country) %>% summarise(avgWorkHour = mean(WorkHour))

df_select_fixed <- inner_join(df_select1 , df_select2 , by = c("Country" = "Country"))

df_final <- inner_join(df_select_fixed, url_table , by = c("Country" = "region"))

```

##gather

```{r}
library(tidyverse)

df_final <- gather(df_final, Both, Male, Female, key = "Sex" , value = "NumberOfSuicide")


ggplot(df_final , aes(x = avgWorkHour , y = NumberOfSuicide, colour = Sex)) +xlab("Weekly Working Hour") + ylab("Number of Suicide") + geom_point() + geom_smooth()

ggplot(df_final , aes(x = avgIncome , y = NumberOfSuicide , colour = Sex)) + xlab("Annual Income") + ylab("Number of Suicide") + geom_point() + geom_smooth()

```
